Approximation as Differentiation notes

### 2025-02-22 notes/definitions.tex
Tweakery.

\todo{Some properties of $\Fam(C)$.}

@@

\noindent $\LatGal$ has finite biproducts. \todo{Tie this to pre-additive structure.}

@@

We note that if a category $C$ is \emph{$\CMon$-enriched}, then:
\begin{enumerate}
\item every hom-object $\Hom{C}{A}{B}$ is a commutative monoid (writing $\zero_{A,B}$ for the unit and
$+_{A,B}$ for the binary operation);
\item composition is given by a family of morphisms $\Hom{C}{B}{C} \tensor \Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in
$\CMon$, i.e.~satisfies

@@

$\CMon$ is closed monoidal, and so enriched over itself. Every hom-object $\CMon(A,B)$ is a commutative
monoid, with:
\begin{enumerate}
\item unit given by the constant homomorphism sending every element of $A$ to $\varepsilon_B$;
\item binary operation given pointwise so that $(f + g)(a) = f(a) + f(b)$.
\end{enumerate}

@@

If $C$ is $\CMon$-enriched then any functor category $\Func{D}{C}$ is $\CMon$-enriched.

@@

A presheaf $F: \LatGal^\op \to \CMon$ assigns to every bounded lattice $L$ a commutative monoid $FL$ and to
every Galois connection $f: L \to L'$ . $\Func{\LatGal^\op}{\CMon}$ is the category of presheaves of
commutative monoids on $\LatGal$.

>>>>

@@

\noindent $\LatGal$ has finite biproducts.

@@

We note that if a category $C$ is \emph{$\CMon$-enriched}, then:
\begin{enumerate}
\item every hom-object $\Hom{C}{A}{B}$ is a commutative monoid (writing $\zero_{A,B}$ for the unit and
$+_{A,B}$ for the binary operation);
\item composition is \emph{biadditive}, i.e.~given by a family of morphisms $\Hom{C}{B}{C} \tensor
\Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in $\CMon$ that preserve the additive structure in $\Hom{C}{B}{C}$ and
$\Hom{C}{A}{B}$ separately:

@@

$\CMon$ is closed monoidal, and so enriched over itself; every hom-object $\CMon(A,B)$ is a commutative
monoid with:
\begin{enumerate}
\item unit given by the constant homomorphism sending every element of $A$ to $\varepsilon_B$;
\item binary operation given pointwise so that $(f + g)(a) = f(a) + f(b)$.
\end{enumerate}

@@

\begin{proposition}
If $C$ is $\CMon$-enriched then any functor category $\Func{D}{C}$ is $\CMon$-enriched.
\end{proposition}

@@

A presheaf $F: \LatGal^\op \to \CMon$ assigns to every bounded lattice $L$ a commutative monoid $F(L)$ and to
every Galois connection $f: L \to L'$ a commutative monoid homomorphism $F(f): F(L) \to F(L')$.
$\Func{\LatGal^\op}{\CMon}$ is the category of presheaves of commutative monoids on $\LatGal$.
